---
title: "GMM o ASE"
author: "YP"
date: "8/7/2017"
output: 
    html_document:
      keep_md: yes
      theme: cerulean
      number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Codes and Demos

Example codes are in the `demo` folder at [github](https://github.com/youngser/gmmase).

## `R` Package

The latest `R` source package can be installed via `github` as

```{r echo=TRUE, eval=FALSE}
require(devtools)
devtools::install_github("youngser/gmmase")
```

## Demos

The package contains a couple of demos. They do

1. generate or read a graph,
2. do a graph spectral embedding (ASE),
3. run `mclust` (GMM).

```{r demo, eval=FALSE}
library(gmmase)

# a toy graph with 100 vertices
demo(toygraph)

# a larger graph with 10,000 vertices
demo(usergraph)
```

To use a user graph, please try this (as shown in the code in `demo/usergraph.R`)

```{r user, eval=FALSE}
fname <- readline(prompt="Enter a file name (e.g., /path/edgelist.txt): ")
g <- read_graph(fname, format="edgelist") # please read igraph manual page for details.
```

The outputs of the demos are here:

* [toygraph](http://www.cis.jhu.edu/~parky/gmmase/demo/toygraph.html)
* [usergraph](http://www.cis.jhu.edu/~parky/gmmase/demo/usergraph.html)

# Software and Hardware Information

```{r vn,echo=TRUE, eval=TRUE}
library(help='gmmase')
sessionInfo()
```

-----
*prepared by <youngser@jhu.edu> on `r date()`*

