---
title: "GMM o ASE"
author: "Department of Applied Mathematics and Statistics <br /> Johns Hopkins University"
date: "`r date()`"
output: 
    html_document:
      keep_md: yes
      css: ~/RFolder/pandoc.css
      theme: cerulean
      number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Codes and Demos

Example codes are in the `demo` folder at [github](https://github.com/youngser/gmmase).

## `R` Package

The latest `R` source package can be installed via `github` as

```{r echo=TRUE, eval=FALSE}
require(devtools)
devtools::install_github("youngser/gmmase")
```

## Demos

The package contains a couple of demos. They do

1. generate or read a graph,
2. do a _pass-to-rank_ for a directed graph (`PTR`, no-op for an unweighted graph),
3. do a graph spectral embedding (`ASE`),
4. do a dimension reduction (`ZG`) and merge left and right vectors (no-op for an unweighted graph),
5. run `mclust` (`GMM`).

```{r demo, eval=FALSE}
library(gmmase)

# a toy graph with 100 vertices
demo(toygraph)

# a larger graph with 10,000 vertices: may take a few minutes, depending on the system
demo(usergraph)
```

The outputs of the demos are here:

* [toygraph](http://www.cis.jhu.edu/~parky/gmmase/demo/toygraph.html)
* [usergraph](http://www.cis.jhu.edu/~parky/gmmase/demo/usergraph.html)

To use a user graph, please try this (as shown in the code in `demo/usergraph.R`)

```{r user, eval=FALSE}
fname <- readline(prompt="Enter a file name (e.g., /path/edgelist.txt): ")
g <- read_graph(fname, format="edgelist") # please read igraph manual page for details, e.g., other graph formats it can handle, etc.
```


# Software and Hardware Information

```{r vn,echo=TRUE, eval=TRUE}
library(help='gmmase')
sessionInfo()
```

-----
*prepared by <youngser@jhu.edu> on `r date()`*

