---
title: "Graph Spectral Clustering"
author: "Department of Applied Mathematics and Statistics <br /> Johns Hopkins University"
date: "`r date()`"
output: 
    html_document:
      keep_md: yes
      css: ~/RFolder/pandoc.css
      theme: cerulean
      number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Codes and Demos

This is an `R` package that does

1. generate or read a graph,
2. do a _pass-to-rank_ for a weighted graph (`PTR`, no-op for an unweighted graph),
3. do a _graph spectral embedding_ (`ASE` or `LSE`) with a _diagonal augmentation_,
4. do a _dimension reduction_ (`ZG`) and merge left and right vectors (no-op for an undirected graph),
5. cluster vertices (`GMM` or `Kmeans`).

## `R` Package

The latest `R` source package can be installed via `github` as

```{r echo=TRUE, eval=FALSE}
require(devtools)
devtools::install_github("youngser/gmmase")
```

## Demos

Example codes are in the `demo` folder at [github](https://github.com/youngser/gmmase), which can be run via

```{r demo, eval=FALSE}
library(gmmase)

# a toy graph with 100 vertices
demo(toygraph)

# a larger graph with 10,000 vertices: may take a few minutes, depending on the system
demo(usergraph)
```

The outputs of the demos are here:

* [toygraph](http://www.cis.jhu.edu/~parky/gmmase/demo/toygraph.html)
* [usergraph](http://www.cis.jhu.edu/~parky/gmmase/demo/usergraph.html)

## User data

To use a user graph, please try this (as shown in the code in `demo/usergraph.R`):

```{r user, eval=FALSE}
fname <- readline(prompt="Enter a file name (e.g., /path/edgelist.txt): ")
g <- read_graph(fname, format="edgelist") 
E(g)$weight <- runif(ecount(g), 1, 5) # add random edge weights
Y <- gmmase(g, dmax=20, use.ptr=TRUE, embed="ASE", clustering="GMM")
```

where

* `embed` can be either "ASE" or "LSE", and
* `clustering` can be either "GMM" or "Kmeans", where
    + "GMM" yields BIC curve, and
    + "Kmeans" yields ASW curve.


The output of `gmmase` function is a clustering label vector.

Also, please refer to the `igraph`'s [manual page](http://igraph.org/r/doc/read_graph.html) for details about other graph formats it can handle.

# Software and Hardware Information

```{r gmmase, echo=TRUE, eval=TRUE, cache=FALSE}
library(help='gmmase')
sessionInfo()
```

-----
*prepared by <youngser@jhu.edu> on `r date()`*

