---
title: "`r_49`: Facebook Relationship Prediction"
author: "JHU Team"
date: "`r Sys.Date()`"
output: 
    rmarkdown::html_vignette:
        toc: yes
        fig_caption: yes
  pdf_document:
    fig_caption: yes
    fig_crop: no
    keep_tex: yes
    number_sections: yes
    toc: yes
vignette: >
  \VignetteIndexEntry{Vignette Title}
  \VignetteEncoding{UTF-8}
  \VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, results='asis'}
source("~/Dropbox/Worm/Codes/Connectome/mbstructure/R/structure-utils.R")
#source("http://www.cis.jhu.edu/~parky/Semipar_vs_Nonpar/utils.r")
source("~/Dropbox/RFiles/ccc_utils.R")

suppressMessages(library(knitr))
#opts_knit$set(animation.fun = hook_scianimator)

#suppressMessages(library(tourr))
#suppressMessages(library(animint))
suppressMessages(library(RColorBrewer))
```

# Problem 

GM250_seed is an instance of the Graph Matching problem.   
In this problem two graphs are given. `G1` and `G2`.  
A partial map between nodes of `G1` and `G2` are provided in the train data.  
The task is to predict the mapping between the unmapped nodes in the test data.

# Data

Data for GM250_seed consists of two graphs in raw_data dir:  

* `G1.gml`: attributed undirected graph; ~~250~~ 755 nodes; 5138 edges; ~~12~~ 4 features for each node
* `G2.gml`: attributed undirected graph; ~~124~~ 755 nodes; ~~324~~ 5138 edges; ~~12~~ 4 features for each node
* `trainData.csv` contains `G1` nodes and `trainTargets.csv` contains `G2` nodes. Together, they constitute 151 known mappings.
* ~~`testData.csv` contains `G2` nodes, for which the mappings have to be predicted in `testTargets.csv`~~

```{r data, fig.show='hold', fig.width=7, fig.height=7, comment="#"}
suppressMessages(library(tidyverse))
suppressMessages(library(igraph))
suppressMessages(library(Matrix))
suppressMessages(library(VN))

dtifile <- "~/Dropbox/D3M/D3M/connectome_stats/dwimean_3216.edgelist"
mrifile <- "~/Dropbox/D3M/D3M/connectome_stats/fmrimean_2039.edgelist"

dtidat <- read.table(dtifile)
mridat <- read.table(mrifile)
gdti <- graph_from_edgelist(as.matrix(dtidat)[,-3], directed=FALSE); 
E(gdti)$weight <- dtidat[,3]; summary(gdti); is.connected(gdti)
gmri <- graph_from_edgelist(as.matrix(mridat)[,-3], directed=FALSE); 
E(gmri)$weight <- mridat[,3]; summary(gmri); is.connected(gmri)
```

```{r gmmase, message=FALSE, comment="#"}
out1 <- gmmase(gdti, dmax = 20, embed = "ASE", Kmax = 10, clustering = "GMM", verbose=FALSE)
#out1 <- gmmase(g, dmax = 100, embed = "LSE", Kmax = 10, clustering = "GMM", verbose=FALSE)
#out1 <- gmmase(g, dmax = 100, embed = "ASE", Kmax = 10, clustering = "Kmeans", verbose=FALSE)

Xhat1 <- out1$mc$data
Yhat <- out1$Y
df2 <- data.frame(Xhat=Xhat1, cluster=as.factor(Yhat))
ggpairs(df2, columns=1:(ncol(df2)-2), mapping=aes(color=cluster, alpha=0.5))
```

```{r perm, comment="#"}
# rearrange the graphs so that seeds are the first m vertices
matched.id1 <- match(train$G1.nodeID, V(g1)$nodeID) # 151
perm.g1 <- invPerm(c(matched.id1, (1:vcount(g1))[-matched.id1]))
matched.id2 <- unique(match(train$G2.nodeID, V(g2)$nodeID)) # 145
perm.g2 <- invPerm(c(matched.id2, (1:vcount(g2))[-matched.id2]))
g1.new <- permute.vertices(g1, perm.g1)
g2.new <- permute.vertices(g2, perm.g2)
g2.sub <- induced.subgraph(g2.new, 1:nrow(train)); summary(g2.sub)
```

# Seeded Graph Matching 

So, `m` = `r nrow(train)` correspondence are given.  
We will use the first $s = \{0,30,60,90,120, 150\}$ vertices as seeds and repeat the process 100 times to see the matching performance.


>On Sep 9, 2017, at 12:18 PM, Vince Lyzinski <vincelyzinski@gmail.com> wrote:
>
>hard seeding enforces the seeds throughout the problem (they can't change), while
soft seeding just initializes at the seeds, but allows them to change in the course of the optimization


```{r sgmno, echo=FALSE, eval=FALSE}
A1 <- as.matrix(g1.new[])
A2 <- as.matrix(g2.new[])
n <- nrow(A1)
m <- nrow(A2)
gamma <- 1
s <- 10 # numseed
M <- rsp(n-s,gamma)
S <- diag(n);
S[(s+1):n,(s+1):n] <- M
system.time(out <- sgm(A2, A1, 0, start=S, pad=0, iteration=30))
newA2 <- out$P %*% A1 %*% t(out$P)
(f <- norm(A2[1:m,1:m]-newA2[1:m,1:m], "F"))
(matchV <- sum(out$corr[1:m] == 1:m))
#The accuracy for the first `m` = `r m` vertices is `r matchV`, which is `r matchV/m`%.
```


```{r sim, echo=TRUE, eval=TRUE}
set.seed(12345)

A1 <- as.matrix(g1.new[])
A2 <- as.matrix(g2.new[])
n <- nrow(A1)
m <- nrow(A2)
gamma <- 1

nmc <- 100
niter <- 30
svec <- seq(0, 150, by=30)
```
```{r sgm, echo=TRUE, eval=FALSE}
method <- "hard"

for (s in svec) {
    cat("Working on s = ", s, "\n")
    mc <- foreach (i=1:nmc) %dopar% {
        ## S is a starting point for softseeding
        if (method=="soft") {
            M <- rsp(n-s,gamma)
            S <- diag(n);
            S[(s+1):n,(s+1):n] <- M
            out <- sgm(A2,A1,0,start=S,pad=0,iteration=niter)
        } else { # "hard"
            S <-matrix(1/(n-s), n-s, n-s) 
            out <- sgm(A2,A1,s,start=S,pad=0,iteration=niter)
            if (s > 0) {
                out$corr <- c(1:s,out$corr)  
            }
        }
        
        newA2 <- out$P %*% A1 %*% t(out$P)
        f <- norm(A2[1:m,1:m]-newA2[1:m,1:m], "F")
        matchV <- sum(out$corr[1:m] == 1:m)
        matchE <- sum((A2[1:m,1:m]+newA2[1:m,1:m])>=2) / 2
        c(matchV, matchE, f)
    }
    save(mc,n,m,nmc,s,gamma,file=paste0("mc-r49-s",s,"-nmc",nmc,"-niter",niter,"-",method,".Rbin"))
}
```
```{r acollect21,echo=FALSE, fig.show='hold', fig.width=7, fig.height=7, comment="#"}
matchV <- matchE <- f <- NULL
for (s in svec) {
    load(paste0("~/Dropbox/D3M/D3M/r49/mc-r49-s",s,"-nmc",nmc,"-niter",niter,".Rbin"))
    matchV <- c(matchV, unlist(sapply(mc,"[",1)))
    matchE <- c(matchE, unlist(sapply(mc,"[",2))/2)
    f <- c(f, unlist(sapply(mc,"[",3)))
}

df <- data.frame(init=rep(1:nmc,times=length(svec)),
                 f=f, matchV=matchV, matchE=matchE,
                 s=factor(rep(svec, each=nmc)))

df3 <- df %>% group_by(s) %>% arrange(f) %>% mutate(init2=order(f)) %>% select(-init)

# "hard"
niter <- 30
matchV <- matchE <- f <- NULL
for (s in svec) {
    load(paste0("~/Dropbox/D3M/D3M/r49/mc-r49-s",s,"-nmc1-niter",niter,"-hard.Rbin")); nmc=100
    matchV <- c(matchV, rep(unlist(sapply(mc,"[",1)),nmc))
    matchE <- c(matchE, rep(unlist(sapply(mc,"[",2)),nmc))
    f <- c(f, rep(unlist(sapply(mc,"[",3)),nmc))
}

df <- data.frame(init=rep(1:nmc,times=length(svec)),
                 f=f, matchV=matchV, matchE=matchE,
                 s=factor(rep(svec, each=nmc)))

df32 <- df %>% group_by(s) %>% arrange(f) %>% mutate(init2=order(f)) %>% select(-init)

df33 <- rbind(data.frame(method="soft", df3), data.frame(method="hard", df32))

df4 <- gather(df33, key="variable", value="value", -c(s,init2,method))

ggplot(df4, aes(x=init2,y=value)) +
    facet_grid(variable~., scales="free") + xlab("initialization") +
#    geom_point(aes(col=s, shape=method)) +
    geom_line(aes(col=s, linetype=method), size=1.2) + 
#    scale_color_brewer(palette = "Set1") +
    theme(text=element_text(size=12)) + 
    theme(strip.text=element_text(size=rel(1.1))) +
    theme(legend.title=element_text(size=rel(1.1),face="bold")) + labs(color="seeds") +
    theme(legend.text=element_text(size=rel(1.0),face="plain"))
```
